Thesis outline

### 2017-06-17 KellyDouglass/Thesis/Thesis_sections/Paper2.tex
Added acknowledgments and dedication

\chapter[N/O ratio in dwarf galaxies]{Large-scale environmental dependence of the abundance ratio of nitrogen to oxygen in blue, star-forming galaxies fainter than $L_*$}\label{ch:Paper2}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    THEORY
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Theory]{Estimation of gas-phase chemical abundances from optical spectroscopy}
\label{sec:Theory}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper2/NIIOIII_energy_level_diagram-figure0}
    \caption[{[\ion{O}{3}] and [\ion{N}{2}] energy-level diagram}]{Energy-level 
    diagram for [\ion{O}{3}] and [\ion{N}{2}] $(2p^2)$ ions.  The most important 
    transitions are shown; all are in the visible spectrum.  These forbidden 
    transitions in both oxygen and nitrogen provide an estimate of the electron 
    temperature in the interstellar gas.  Because oxygen is more abundant, we 
    use the oxygen lines to estimate the temperature of the gas.}
    \label{fig:transitions_P2}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    DATA
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Data]{SDSS data and galaxy selection}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    ANALYSIS & RESULTS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Results]{Abundance analysis and results}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_logNpOp_logNO_fit}
    \caption[N/O versus N$^+$/O$^+$]{Comparison of the N/O and N$^+$/O$^+$ 
    abundance ratios for our dwarf galaxies.  Brighter galaxies ($M_r > -20$) 
    are shown in gray for context.  All our star-forming galaxies with 
    $M_r > -20$ roughly follow the approximation that N/O $\cong$ N$^+$/O$^+$, 
    which is often assumed in other studies of the abundance ratio of nitrogen 
    to oxygen.  In this paper, we will be using the abundance ratio N/O for our 
    analysis.}
    \label{fig:NO_NpOp}
\end{figure}

@@

	\begin{tabu} to 0.75\textwidth {ccccccccc}
	    Abs. Mag. Range & Environment & \# of Galaxies & Average & Median & Average Shift\footnote[1]{Wall -- Void (positive shifts indicate that the wall values are greater than the void values; negative shifts indicate that the void values are greater than the wall values)} & Median Shift\footnote[1] & K-S Test Statistic & $p$-value \\
	    \hline
	    \hline
        % Oxygen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \multicolumn{9}{c}{\OH}\\
        \hline
        \multirow{2}{*}{Dwarf galaxies} & Void & 42 & $7.99\pm 0.049$ & 8.04 & \multirow{2}{*}{$-0.07\pm 0.060$} & \multirow{2}{*}{-0.03} & \multirow{2}{*}{0.1322} & \multirow{2}{*}{0.6701}\\
         & Wall & 89 & $7.93\pm 0.036$ & 8.01 & & & & \\
        \multirow{2}{*}{$-17>M_r>-18$} & Void & 423 & $7.87\pm 0.016$ & 7.96 & \multirow{2}{*}{$0.01\pm 0.020$} & \multirow{2}{*}{-0.02} & \multirow{2}{*}{0.0455} & \multirow{2}{*}{0.5799}\\
         & Wall & 895 & $7.88\pm 0.012$ & 7.94 & & & & \\
        \multirow{2}{*}{$-18>M_r>-19$} & Void & 829 & $7.74\pm 0.013$ & 7.76 & \multirow{2}{*}{$-0.01\pm 0.016$} & \multirow{2}{*}{-0.04} & \multirow{2}{*}{0.0385} & \multirow{2}{*}{0.4000}\\
         & Wall & 1498 & $7.73\pm 0.009$ & 7.73 & & & & \\
        \multirow{2}{*}{$-19>M_r>-20$} & Void & 798 & $7.59\pm 0.013$ & 7.55 & \multirow{2}{*}{$-0.04\pm 0.017$} & \multirow{2}{*}{-0.05} & \multirow{2}{*}{0.0741} & \multirow{2}{*}{0.0062}\\
         & Wall & 1490 & $7.55\pm 0.010$ & 7.50 & & & & \\
        \hline
        % Nitrogen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \multicolumn{9}{c}{\NH}\\
        \hline
        \multirow{2}{*}{Dwarf galaxies} & Void & 42 & $6.74\pm 0.035$ & 6.77 & \multirow{2}{*}{$-0.02\pm 0.043$} & \multirow{2}{*}{-0.01} & \multirow{2}{*}{0.1129} & \multirow{2}{*}{0.8383}\\
         & Wall & 89 & $6.72\pm 0.025$ & 6.75 & & & & \\
        \multirow{2}{*}{$-17>M_r>-18$} & Void & 423 & $6.80\pm 0.011$ & 6.82 & \multirow{2}{*}{$0.00\pm 0.014$} & \multirow{2}{*}{-0.01} & \multirow{2}{*}{0.0401} & \multirow{2}{*}{0.7364}\\
         & Wall & 895 & $6.80\pm 0.008$ & 6.81 & & & & \\
        \multirow{2}{*}{$-18>M_r>-19$} & Void & 829 & $6.87\pm 0.009$ & 6.85 & \multirow{2}{*}{$0.01\pm 0.011$} & \multirow{2}{*}{0.02} & \multirow{2}{*}{0.0538} & \multirow{2}{*}{0.0873}\\
         & Wall & 1498 & $6.89\pm 0.007$ & 6.87 & & & & \\
        \multirow{2}{*}{$-19>M_r>-20$} & Void & 798 & $6.97\pm 0.009$ & 6.94 & \multirow{2}{*}{$-0.02\pm 0.011$} & \multirow{2}{*}{-0.02} & \multirow{2}{*}{0.0455} & \multirow{2}{*}{0.2272}\\
         & Wall & 1490 & $6.95\pm 0.007$ & 6.93 & & & & \\
        \hline
        % N/O %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \multicolumn{9}{c}{\NO}\\
        \hline
        \multirow{2}{*}{Dwarf galaxies} & Void & 42 & $-1.25\pm 0.060$ & -1.28 & \multirow{2}{*}{$0.05\pm 0.074$} & \multirow{2}{*}{0.07} & \multirow{2}{*}{0.2191} & \multirow{2}{*}{0.1116}\\
         & Wall & 89 & $-1.21\pm 0.044$ & -1.22 & & & & \\
        \multirow{2}{*}{$-17>M_r>-18$} & Void & 423 & $-1.08\pm 0.020$ & -1.13 & \multirow{2}{*}{$-0.00\pm 0.024$} & \multirow{2}{*}{0.04} & \multirow{2}{*}{0.0588} & \multirow{2}{*}{0.2657}\\
         & Wall & 895 & $-1.08\pm 0.014$ & -1.09 & & & & \\
        \multirow{2}{*}{$-18>M_r>-19$} & Void & 829 & $-0.86\pm 0.015$ & -0.88 & \multirow{2}{*}{$0.02\pm 0.019$} & \multirow{2}{*}{0.03} & \multirow{2}{*}{0.0550} & \multirow{2}{*}{0.0763}\\
         & Wall & 1498 & $-0.84\pm 0.012$ & -0.85 & & & & \\
        \multirow{2}{*}{$-19>M_r>-20$} & Void & 798 & $-0.62\pm 0.016$ & -0.62 & \multirow{2}{*}{$0.02\pm 0.020$} & \multirow{2}{*}{0.02} & \multirow{2}{*}{0.0564} & \multirow{2}{*}{0.0715}\\
         & Wall & 1490 & $-0.60\pm 0.012$ & -0.60 & & & & \\
         \hline
	\end{tabu}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_Z12logOH_logNO}
    \caption[N/O versus metallicity of 135 dwarf galaxy sample]{N/O as a 
    function of O/H for star-forming void (red circles) and wall (black 
    triangles) dwarf galaxies.  Error bars have been omitted for clarity.  N/O 
    is expected to be constant for $12 + \log (\text{O}/\text{H}) \lesssim 8.5$, 
    as the metallicity of a galaxy's ISM is too low for stars to be created with 
    enough of the heavy elements to undergo the CNO cycle early enough in their 
    lifetimes.  As a result, nitrogen behaves as a primary element at galactic 
    metallicities less than approximately 8.5.  To place the dwarf galaxies in 
    the context of the general galaxy population, we also plot (gray stars) all 
    star-forming galaxies fainter than $M_r > -20$.}
    \label{fig:OvN}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_Z12logOH_N12logNH}
    \caption[N/H versus metallicity for 135 dwarf galaxy sample]{N/H as a 
    function of O/H for star-forming void (red circles) and wall (black 
    triangles) dwarf galaxies.  Error bars have been omitted for clarity.  There 
    is a positive correlation between the two abundances.  With a best-fit slope 
    less than 1, we see that the synthesis of nitrogen in these galaxies is 
    primary.}
    \label{fig:OHvNH}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{Images/Paper2/MNO_1sig_I06_dwarf_0-20_SF_t3}
    \caption[Stellar mass versus N/O for 135 dwarf galaxy sample]{Mass--N/O 
    relation for star-forming void (red circles) and wall (black triangles) 
    dwarf galaxies.  Error bars have been omitted for clarity.  N/O is expected 
    to remain constant for low stellar masses and increase steadily for larger 
    masses, due to the mass-metallicity relation and the primary vs. secondary 
    synthesis of nitrogen.  To place the dwarf galaxies in the context of the 
    general galaxy population, we also plot (gray stars) the star-forming 
    galaxies with $M_r > -20$.}
    \label{fig:MNO}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    DISCUSSION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Discussion]{Large-scale environmental influence}\label{sec:environment}

>>>>

\chapter[N/O Ratio in Dwarf Galaxies]{Large-Scale Environmental Dependence of the Abundance Ratio of Nitrogen to Oxygen in Blue, Star-Forming Galaxies Fainter than $L_*$}\label{ch:Paper2}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    THEORY
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Calculating N/H \& N/O]{Estimation of gas-phase chemical abundances from optical spectroscopy}
\label{sec:Theory}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper2/NIIOIII_energy_level_diagram-figure0}
    \caption[{[\ion{O}{3}] and [\ion{N}{2}] energy-level diagram}]{Energy-level 
    diagram for [\ion{O}{3}] and [\ion{N}{2}] $(2p^2)$ ions.  The most important 
    transitions are shown; all are in the visible spectrum.  These forbidden 
    transitions in both oxygen and nitrogen provide an estimate of the electron 
    temperature in the interstellar gas.  Because oxygen is more abundant, we 
    use the oxygen lines to estimate the temperature of the gas.}
    \label{fig:transitions_P2}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    DATA
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[SDSS Data]{SDSS data and galaxy selection}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    ANALYSIS & RESULTS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Analysis \& Results]{Abundance analysis and results}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_logNpOp_logNO_fit}
    \caption[N/O versus N$^+$/O$^+$]{Comparison of the N/O and N$^+$/O$^+$ 
    abundance ratios for our dwarf galaxies.  Brighter galaxies ($M_r > -20$) 
    are shown in gray for context.  All our star-forming galaxies with 
    $M_r > -20$ roughly follow the approximation that N/O $\cong$ N$^+$/O$^+$, 
    which is often assumed in other studies of the abundance ratio of nitrogen 
    to oxygen.  In this paper, we will be using the abundance ratio N/O for our 
    analysis.}
    \label{fig:NO_NpOp}
\end{figure}

@@

	\begin{tabular}{ccccccccc}
	    Abs. Mag. Range & Environment & \# of Galaxies & Average & Median & Average Shift\footnote{Wall -- Void (positive shifts indicate that the wall values are greater than the void values; negative shifts indicate that the void values are greater than the wall values)\label{fnote_P2}} & Median Shift\textsuperscript{\ref{fnote_P2}} & K-S Test Statistic & $p$-value \\
	    \hline
	    \hline
        % Oxygen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \multicolumn{9}{c}{\OH}\\
        \hline
        \multirow{2}{*}{Dwarf galaxies} & Void & 42 & $7.99\pm 0.049$ & 8.04 & \multirow{2}{*}{$-0.07\pm 0.060$} & \multirow{2}{*}{-0.03} & \multirow{2}{*}{0.1322} & \multirow{2}{*}{0.6701}\\
         & Wall & 89 & $7.93\pm 0.036$ & 8.01 & & & & \\
        \multirow{2}{*}{$-17>M_r>-18$} & Void & 423 & $7.87\pm 0.016$ & 7.96 & \multirow{2}{*}{$0.01\pm 0.020$} & \multirow{2}{*}{-0.02} & \multirow{2}{*}{0.0455} & \multirow{2}{*}{0.5799}\\
         & Wall & 895 & $7.88\pm 0.012$ & 7.94 & & & & \\
        \multirow{2}{*}{$-18>M_r>-19$} & Void & 829 & $7.74\pm 0.013$ & 7.76 & \multirow{2}{*}{$-0.01\pm 0.016$} & \multirow{2}{*}{-0.04} & \multirow{2}{*}{0.0385} & \multirow{2}{*}{0.4000}\\
         & Wall & 1498 & $7.73\pm 0.009$ & 7.73 & & & & \\
        \multirow{2}{*}{$-19>M_r>-20$} & Void & 798 & $7.59\pm 0.013$ & 7.55 & \multirow{2}{*}{$-0.04\pm 0.017$} & \multirow{2}{*}{-0.05} & \multirow{2}{*}{0.0741} & \multirow{2}{*}{0.0062}\\
         & Wall & 1490 & $7.55\pm 0.010$ & 7.50 & & & & \\
        \hline
        % Nitrogen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \multicolumn{9}{c}{\NH}\\
        \hline
        \multirow{2}{*}{Dwarf galaxies} & Void & 42 & $6.74\pm 0.035$ & 6.77 & \multirow{2}{*}{$-0.02\pm 0.043$} & \multirow{2}{*}{-0.01} & \multirow{2}{*}{0.1129} & \multirow{2}{*}{0.8383}\\
         & Wall & 89 & $6.72\pm 0.025$ & 6.75 & & & & \\
        \multirow{2}{*}{$-17>M_r>-18$} & Void & 423 & $6.80\pm 0.011$ & 6.82 & \multirow{2}{*}{$0.00\pm 0.014$} & \multirow{2}{*}{-0.01} & \multirow{2}{*}{0.0401} & \multirow{2}{*}{0.7364}\\
         & Wall & 895 & $6.80\pm 0.008$ & 6.81 & & & & \\
        \multirow{2}{*}{$-18>M_r>-19$} & Void & 829 & $6.87\pm 0.009$ & 6.85 & \multirow{2}{*}{$0.01\pm 0.011$} & \multirow{2}{*}{0.02} & \multirow{2}{*}{0.0538} & \multirow{2}{*}{0.0873}\\
         & Wall & 1498 & $6.89\pm 0.007$ & 6.87 & & & & \\
        \multirow{2}{*}{$-19>M_r>-20$} & Void & 798 & $6.97\pm 0.009$ & 6.94 & \multirow{2}{*}{$-0.02\pm 0.011$} & \multirow{2}{*}{-0.02} & \multirow{2}{*}{0.0455} & \multirow{2}{*}{0.2272}\\
         & Wall & 1490 & $6.95\pm 0.007$ & 6.93 & & & & \\
        \hline
        % N/O %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \multicolumn{9}{c}{\NO}\\
        \hline
        \multirow{2}{*}{Dwarf galaxies} & Void & 42 & $-1.25\pm 0.060$ & -1.28 & \multirow{2}{*}{$0.05\pm 0.074$} & \multirow{2}{*}{0.07} & \multirow{2}{*}{0.2191} & \multirow{2}{*}{0.1116}\\
         & Wall & 89 & $-1.21\pm 0.044$ & -1.22 & & & & \\
        \multirow{2}{*}{$-17>M_r>-18$} & Void & 423 & $-1.08\pm 0.020$ & -1.13 & \multirow{2}{*}{$-0.00\pm 0.024$} & \multirow{2}{*}{0.04} & \multirow{2}{*}{0.0588} & \multirow{2}{*}{0.2657}\\
         & Wall & 895 & $-1.08\pm 0.014$ & -1.09 & & & & \\
        \multirow{2}{*}{$-18>M_r>-19$} & Void & 829 & $-0.86\pm 0.015$ & -0.88 & \multirow{2}{*}{$0.02\pm 0.019$} & \multirow{2}{*}{0.03} & \multirow{2}{*}{0.0550} & \multirow{2}{*}{0.0763}\\
         & Wall & 1498 & $-0.84\pm 0.012$ & -0.85 & & & & \\
        \multirow{2}{*}{$-19>M_r>-20$} & Void & 798 & $-0.62\pm 0.016$ & -0.62 & \multirow{2}{*}{$0.02\pm 0.020$} & \multirow{2}{*}{0.02} & \multirow{2}{*}{0.0564} & \multirow{2}{*}{0.0715}\\
         & Wall & 1490 & $-0.60\pm 0.012$ & -0.60 & & & & \\
         \hline
	\end{tabular}

@@

\begin{figure}
    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_Z12logOH_logNO}
    \caption[N/O versus metallicity of 135 dwarf galaxy sample]{N/O as a 
    function of O/H for star-forming void (red circles) and wall (black 
    triangles) dwarf galaxies.  Error bars have been omitted for clarity.  N/O 
    is expected to be constant for $12 + \log (\text{O}/\text{H}) \lesssim 8.5$, 
    as the metallicity of a galaxy's ISM is too low for stars to be created with 
    enough of the heavy elements to undergo the CNO cycle early enough in their 
    lifetimes.  As a result, nitrogen behaves as a primary element at galactic 
    metallicities less than approximately 8.5.  To place the dwarf galaxies in 
    the context of the general galaxy population, we also plot (gray stars) all 
    star-forming galaxies fainter than $M_r > -20$.}
    \label{fig:OvN}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper2/1sig_I06_dwarf_0-20_SF_t3_Z12logOH_N12logNH}
    \caption[N/H versus metallicity for 135 dwarf galaxy sample]{N/H as a 
    function of O/H for star-forming void (red circles) and wall (black 
    triangles) dwarf galaxies.  Error bars have been omitted for clarity.  There 
    is a positive correlation between the two abundances.  With a best-fit slope 
    less than 1, we see that the synthesis of nitrogen in these galaxies is 
    primary.}
    \label{fig:OHvNH}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.75\textwidth]{Images/Paper2/MNO_1sig_I06_dwarf_0-20_SF_t3}
    \caption[Stellar mass versus N/O for 135 dwarf galaxy sample]{Mass--N/O 
    relation for star-forming void (red circles) and wall (black triangles) 
    dwarf galaxies.  Error bars have been omitted for clarity.  N/O is expected 
    to remain constant for low stellar masses and increase steadily for larger 
    masses, due to the mass-metallicity relation and the primary vs. secondary 
    synthesis of nitrogen.  To place the dwarf galaxies in the context of the 
    general galaxy population, we also plot (gray stars) the star-forming 
    galaxies with $M_r > -20$.}
    \label{fig:MNO}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    DISCUSSION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Environmental influence]{Large-scale environmental influence}\label{sec:environment}
